---
title: "CasualImpact_test"
author: "GB"
date: "February 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
myfile<-file.choose()

```


```{r}
mydata<-read.csv(myfile, header = TRUE)
mydata$ga.date<-as.Date(mydata$ga.date)
sprintf('start date in file: %s', min(mydata$ga.date))
sprintf('end date in file: %s', max(mydata$ga.date))

```




```{r library, message=FALSE, warning=FALSE}
library(CausalImpact)
library(dplyr)
library(lattice)
```


```{r}
paths<-unique(mydata$ga.landingPagePath)
sprintf('total different landing pages: %s', length(paths))
```

## ploting some times series for the random 9 landing Pages, the number can be changed, but keep <12


```{r}
testpaths<-sample(length(paths), 9)
data2<-mydata[mydata$ga.landingPagePath %in% paths[testpaths], ]
xyplot(ga.newUsers~ga.date|ga.landingPagePath, data2)

```

## generating ntiles and plotting ntiles versus counts. counts here are total NewUsers per page. Number of ntiles is 10. can be changed.

```{r ntiles column}
kn=10 # numer of ntiles, can be changed
sumdata<-summarize(group_by(mydata, ga.landingPagePath), counts=n())
sumdata<-sumdata[order(-sumdata$counts), ]
sumdata$ntiles<-ntile(sumdata$counts, kn)
xyplot(ntiles~counts, sumdata)
```



```{r making groups}
kg=7   # kg = to number of test groups 

```



# 
# 
# below is testing the package with synthetic data from the tutorial. this was done to assure that all dependences (supporting sub-packages) are in working condition



```{r trial data, echo=FALSE}
set.seed(1)
x1 <- 100 + arima.sim(model = list(ar = 0.999), n = 100)
y <- 1.02 * x1 + rnorm(100)
y[71:100] <- y[71:100] + 10
data <- cbind(y, x1)
```

```{r}

```

```{r}
matplot(data, type = "l")
#par(cex = 0.85, oma = c(0, 0, 0, 0), mar = c(3, 2, 1, 1))
#matplot(data, type = "l", lwd = 1.5)
```

```{r}
par(cex = 0.85, oma = c(0, 0, 0, 0), mar = c(3, 2, 1, 1))
matplot(data, type = "l", lwd = 1.5)
```
```{r}
pre.period <- c(1, 70)
post.period <- c(71, 100)
```


```{r}
impact <- CausalImpact(data, pre.period, post.period)
```

```{r}
plot(impact)
```

```{r}
library(ggplot2)
```

```{r}
q <- plot(impact) + theme_bw(base_size = 11)
suppressWarnings(plot(q))
```
```{r}
time.points <- seq.Date(as.Date("2014-01-01"), by = 1, length.out = 100)
data <- zoo(cbind(y, x1), time.points)
head(data)
```

```{r}
pre.period <- as.Date(c("2014-01-01", "2014-03-11"))
post.period <- as.Date(c("2014-03-12", "2014-04-10"))
```
```{r}
impact <- CausalImpact(data, pre.period, post.period)
plot(impact)
```

