---
title: "Causal impact study"
author: "GB"
date: "February 5, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Getting data file and setting experiment start, end and rollout times. window pops up  allowing to choose a file. click on it. startime, endtime rolout times below can be changed. 

```{r}
myfile<-file.choose()
startime<-as.Date('2016-04-01')
endtime<-as.Date('2016-06-01')
rolout<-as.Date('2016-09-01')
```

### reading data file, checking if there is data prior to experiment- answer into variable data_for_strata
```{r}
mydata<-read.csv(myfile, header = TRUE)
mydata$ga.date<-as.Date(mydata$ga.date)
sprintf('start date in file: %s', min(mydata$ga.date))
sprintf('end date in file: %s', max(mydata$ga.date))
if (min(mydata$ga.date) >= startime) { print('Warning: no data prior to experiment start!') 
  data_for_strata<-FALSE} else {data_for_strata<-TRUE}
data_for_strata
```




```{r library, message=FALSE, warning=FALSE}
library(CausalImpact)
library(dplyr)
library(lattice)
```


# 2. Getting to know more about the loaded datafile. 
### Selecting only data from time period before the experiment start as described in Etsy experiment, and plotting it
```{r}
if (data_for_strata==TRUE) {
  prior_to_exp<-mydata[mydata$ga.date < startime,]
  xyplot(ga.newUsers~ga.date, prior_to_exp)
}

```

### Checking how many unique paths are in landingPagePath column

```{r}
paths<-unique(mydata$ga.landingPagePath)   # selects unique landingPagePath's for the entire data file
sprintf('total different landing pages in the entire data file: %s', length(paths))
paths2<-unique(prior_to_exp$ga.landingPagePath) #selects unique landingPagePath's before the experiment
sprintf('total different landing pages prior to experiment: %s', length(paths2))
```

### ploting some times series for the random NP=9 landing Pages, the number can be changed below, NP variable, user selectable


```{r}
NP<-9
testpaths<-sample(length(paths), NP)
data2<-mydata[mydata$ga.landingPagePath %in% paths[testpaths], ]
xyplot(ga.newUsers~ga.date|ga.landingPagePath, data2)
rm(data2)
```

# 3. Building stratas
### Generating ntiles and plotting ntiles versus counts. counts here are total NewUsers per page. Number of ntiles is kn=6. can be changed below, user selectable.

```{r ntiles column}
kn=6 # numer of ntiles, can be changed
sumdata<-summarize(group_by(prior_to_exp, ga.landingPagePath), counts=n()) # getting total counts per landingPagePath
sumdata<-sumdata[order(-sumdata$counts), ]   # ordering in descreasing order
sumdata$ntiles<-ntile(sumdata$counts, kn)  # creating ntiles column and assinging ntile number to each row
xyplot(ntiles~log10(counts), sumdata)
```

### repackaging data into different kg=7 groups. Number kg can be changed. number of unique landingPagePath's per ntile is printed out 


```{r making groups}
kg=7   # kg = to number of test groups 
sumdata$group<-0   #creating group marker column
groupeddata<-data.frame()  # new data frame where results will be
for (i in 1:kn) {   # looping through ntiles
  sampledsumdata<-filter(sumdata, ntiles==i)   # selecting data for specific ntile only
  set.seed(12345)      # 
  sampledsumdata2<-sampledsumdata[sample(nrow(sampledsumdata)),]    # reshufling rows randomly in that table and renaming the table to *2, paths no longer in the same sequence within the landingPath column
  print(length(sampledsumdata$ga.landingPagePath))  # prints the number of paths per ntile
  sampledsumdata2$group<-rep_len(1:kg, length(sampledsumdata2$counts))    # assign group to randomized paths
  groupeddata<-rbind(groupeddata, sampledsumdata2)  # combine into final table
  rm(sampledsumdata, sampledsumdata2)  # remove extra variables
  }

```

## here groupeddata contains landingPagePath, total counts per that path, ntile and group for that landingPagePath. this table is used to map landingPagePath to group in the original data file
```{r adding groups to original file}
x<-groupeddata[match(mydata$ga.landingPagePath,groupeddata$ga.landingPagePath),4,drop=F]
mydata$group<-as.factor(x$group)
rm(x)
```

```{r}
mydata_na<-mydata[!is.na(mydata$group),]   #removes rows with NA in group column, puts result into mydata_na
my.lines<-c(startime, endtime, rolout)
groupmydata<-summarize(group_by(mydata_na, group, ga.date), counts=n()) # agregates per group sum within the group
xyplot(counts~ga.date, groups=group, groupmydata, type='l',auto.key=T, panel = panel.superpose,
       panel.groups = function(..., group.number) {
           panel.abline(v = my.lines[group.number])
           panel.xyplot(...)})
```




## plotting for specific time window, adjust values below:
```{r}
st<-as.Date('2016-03-15')
en<-as.Date('2016-06-15')
groupmydata2<-groupmydata[groupmydata$ga.date<=en & groupmydata$ga.date>st, ]
xyplot(counts~ga.date, groups=group, groupmydata2, type='l', panel = panel.superpose,
       panel.groups = function(..., group.number) {
           panel.abline(v = my.lines[group.number])
           panel.xyplot(...) })
```

 
# 
# 
# below is testing the package with synthetic data from the tutorial. this was done to assure that all dependences (supporting sub-packages) are in working condition



```{r trial data, echo=FALSE}
set.seed(1)
x1 <- 100 + arima.sim(model = list(ar = 0.999), n = 100)
y <- 1.02 * x1 + rnorm(100)
y[71:100] <- y[71:100] + 10
data <- cbind(y, x1)
```

```{r}

```

```{r}
matplot(data, type = "l")
#par(cex = 0.85, oma = c(0, 0, 0, 0), mar = c(3, 2, 1, 1))
#matplot(data, type = "l", lwd = 1.5)
```

```{r}
par(cex = 0.85, oma = c(0, 0, 0, 0), mar = c(3, 2, 1, 1))
matplot(data, type = "l", lwd = 1.5)
```
```{r}
pre.period <- c(1, 70)
post.period <- c(71, 100)
```


```{r}
impact <- CausalImpact(data, pre.period, post.period)
```

```{r}
plot(impact)
```

```{r}
library(ggplot2)
```

```{r}
q <- plot(impact) + theme_bw(base_size = 11)
suppressWarnings(plot(q))
```
```{r}
time.points <- seq.Date(as.Date("2014-01-01"), by = 1, length.out = 100)
data <- zoo(cbind(y, x1), time.points)
head(data)
```

```{r}
pre.period <- as.Date(c("2014-01-01", "2014-03-11"))
post.period <- as.Date(c("2014-03-12", "2014-04-10"))
```
```{r}
impact <- CausalImpact(data, pre.period, post.period)
plot(impact)
```

